---
output:
  word_document: default
  html_document: default
---
#This script prepares Muser data export files to be sent to the Registrar's Office

## File created: 8/29/2022
###Author: Kim Manturuk

```{r include=FALSE}
library(tidyverse)
library(esquisse)
library(readr)
```


### Step 1: Import Applications file and select mentor ID variable
Note - the code below is for the 2022_Spring_2_Applicatons file; update the file path as needed.

```{r}


X2022_Spring_2_Applications <- read_csv("~/Desktop/Muser/Muser Data Library/Data Files RAW/2022_Spring_2_Applications.csv")

X2022_Spring_2_Applications_Registrar_Mentors <- select(X2022_Spring_2_Applications, "NetID (Mentor)")
X2022_Spring_2_Applications_Registrar_Mentors <- X2022_Spring_2_Applications_Registrar_Mentors[!duplicated(X2022_Spring_2_Applications_Registrar_Mentors),]

str_split_fixed(X2022_Spring_2_Applications$Email...7, "@", n=2)

X2022_Spring_2_Applications[ , 10:11] <- str_split_fixed(X2022_Spring_2_Applications$Email...7, "@", n=2)
X2022_Spring_2_Applications["NetID (Student)"] <- X2022_Spring_2_Applications["V1"]
X2022_Spring_2_Applications <- X2022_Spring_2_Applications[ , ! names(X2022_Spring_2_Applications) %in% c("V1", "V2")]

X2022_Spring_2_Applications_Registrar_Students <- select(X2022_Spring_2_Applications, "NetID (Student)")
X2022_Spring_2_Applications_Registrar_Students <- X2022_Spring_2_Applications_Registrar_Students[!duplicated(X2022_Spring_2_Applications_Registrar_Students),]
```

This creates a data file to be sent to the Registrar with the Mentor NetIDs needed to merge back into the data.

### Step 2: Import ApplicationCounts file and select student ID variable







